---
title: '[Week 12] Simulation Evaluation'
author: Giuliano Sposito
date: '2019-11-26'
categories:
  - evaluation
  - simulation
tags:
  - evaluation
  - simulation
slug: week-12-simulation-evaluation
dropCap: no
displayInMenu: no
displayInList: yes
resources:
- name: featuredImage
  src: "wargames_norad.jpg"
  params:
    description: War Games Norad
params:
  week: 12
  version: 4
---

**Matchup Winner Accuracy: 40%**

<!--more-->

## Historic

| week | Winner Accuracy |
|:----:|:---------------:|
| 12   |       40%       |
| 11   |       60%       |
| 10   |       40%       |
| 9    |       20%       |
| 8    |       60%       |
| 7    |       20%       |
| 6    |      100%       |
| 5    |       80%       |
| 4    |       60%       |
| 3    |       80%       |
| 2    |       60%       |
| 1    |       80%       |

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
# put rnotbook in the same workdir
knitr::opts_knit$set(root.dir = normalizePath(rprojroot::find_rstudio_root_file())) 
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


```{r loadAndDataHandling}
# libs
library(tidyverse)
library(glue)
library(ggimage)
library(knitr)
library(kableExtra)

# PARAMETERS
.week <- params$week
.version <- params$version

# SIMULATION

sim <- readRDS(glue("./data/week{.week}_simulation_v{.version}.rds"))

sim.eval <- sim %>% 
  select ( home.name, home.pts, home.sim.org, away.name, away.pts, away.sim.org) %>% 
  mutate( home.win.org = map2(home.sim.org, away.sim.org, function(.h, .a){
      return(.h>.a)
  })) %>% 
  mutate( away.win.org = map(home.win.org, ~!.x)) %>% 
  mutate( home.win = home.pts>away.pts,
          away.win = !home.win,
          home.win.org.prob = map_dbl(home.win.org, mean),
          away.win.org.prob = map_dbl(away.win.org, mean),
          home.win.pred = home.win.org.prob>.5, 
          away.win.pred = away.win.org.prob>.5)

sim.points <- sim.eval %>%
  select(home.name, home.pts, away.name, away.pts, home.sim.org, away.sim.org) %>% 
  mutate(home.pts.prd = map_dbl(home.sim.org, median),
         away.pts.prd = map_dbl(away.sim.org, median),
         home.pts.prd.min = map_dbl(home.sim.org, quantile, .05),
         away.pts.prd.min = map_dbl(away.sim.org, quantile, .05),
         home.pts.prd.max = map_dbl(home.sim.org, quantile, .95),
         away.pts.prd.max = map_dbl(away.sim.org, quantile, .95)) %>% 
  select(-home.sim.org, -away.sim.org)

sim.pts.eval <- bind_rows(
  sim.points %>% select(starts_with("home")) %>% set_names(gsub("home.", "", names(.))),
  sim.points %>% select(starts_with("away")) %>% set_names(gsub("away.", "", names(.)))
  ) %>% 
  set_names(c("team","real.points", "pred.points", "pred.min", "pred.max"))

```

## Matchups Winner Predictions

```{r matchupWinnerPrediction}
sim.eval %>% 
  mutate( game = paste0(away.name," @ ",home.name) ) %>% 
  mutate( prediction = case_when(home.win.pred==T ~ home.name,
                                 away.win.pred==T ~ away.name) ) %>% 
  mutate( win.prob = case_when(home.win.pred==T ~ home.win.org.prob,
                               away.win.pred==T ~ away.win.org.prob) ) %>%
  mutate( win.prob = paste0(round(100*win.prob,1),"%") ) %>% 
  mutate( who.won = case_when(home.win==T ~ home.name,
                              away.win==T ~ away.name) ) %>% 
  select(game, prediction, win.prob, who.won) %>% 
  kable() %>% 
  kable_styling(font_size = 15)
```

## Score Prediction Chart

```{r scorePredChart}
sim.pts.eval %>% 
  ggplot(aes(x=real.points, y=pred.points, color=team)) +
  geom_point(size=2) +
  geom_errorbar(aes(ymin=pred.min, ymax=pred.max), size=1) +
  geom_abline(intercept=c(0,0), slope=1, color="darkgrey", size=1, linetype="dotted") +
  ggtitle("Pontuação Real x Pontuacao Previsa", subtitle = "90% CI") +
  theme_minimal()
```


## Score Prediction Table

```{r scorePredTable}

sim.pts.eval %>% 
  select(team, real.points, pred.min, pred.points, pred.max) %>%
  mutate_if(is.numeric, round, digits=2) %>% 
  arrange(desc(real.points)) %>% 
  kable()

```

## Players Points vs Projection

```{r errorPlayers}

proj <- readRDS("./data/points_projection.rds")
pts  <- readRDS("./data/players_points.rds")

dtf <- pts %>% 
  inner_join(proj, by=c("id"="id", "week", "season"))  %>% 
  select(id, nfl_id, season, week, pos, data_src, pts.proj, points )  %>% 
  mutate(error=points-pts.proj)


dtf %>% 
  ggplot() +
  geom_point(aes(x=pts.proj, y=points, color=pos)) +
  facet_grid(pos~data_src, scales = "free") +
  geom_abline(intercept=0, slope=1, linetype="dashed") + 
  ggtitle(glue("Projection"), subtitle = "By Position and Source Site") +
  xlim(0,30) + ylim(0,30)

```

## Projection Error Distribution

```{r errorProjection}

dtf %>% 
  ggplot() +
  geom_density(aes(x=error, fill=pos)) +
  facet_grid(pos~data_src, scales = "free") +
  geom_vline(xintercept = 0, color="black", linetype="dashed") +
  ggtitle("Error Distribution", subtitle = "By Position and Source Site") +
  theme_minimal()

```

## Twittersphere

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">My favourite time of the week. The Aaron Rodgers Sack/Fumble. 👌🏻<a href="https://twitter.com/hashtag/GBvsSF?src=hash&amp;ref_src=twsrc%5Etfw">#GBvsSF</a> <a href="https://t.co/iY30cZwubC">pic.twitter.com/iY30cZwubC</a></p>&mdash; Craig Sutherland (@Craigisonfire) <a href="https://twitter.com/Craigisonfire/status/1198776271918026753?ref_src=twsrc%5Etfw">November 25, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Bill Burr break&#39;s down Mason Rudolph&#39;s role in the <a href="https://twitter.com/hashtag/Browns?src=hash&amp;ref_src=twsrc%5Etfw">#Browns</a> vs Steelers fight from last Thursday (wait for it...).<br><br>Audio curtesy of <a href="https://twitter.com/billburr?ref_src=twsrc%5Etfw">@billburr</a>&#39;s podcast: <a href="https://twitter.com/theMMPodcast?ref_src=twsrc%5Etfw">@theMMPodcast</a>. <a href="https://t.co/2giiRSjxZZ">pic.twitter.com/2giiRSjxZZ</a></p>&mdash; Roberto Shenanigans (@Rob_Shenanigans) <a href="https://twitter.com/Rob_Shenanigans/status/1197246262619377670?ref_src=twsrc%5Etfw">November 20, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

