---
title: '[Week 12] Players Projection and Matchups Simulation'
author: 'Giuliano Sposito'
date: '2019-11-21'
categories:
  - projection
  - simulation
tags:
  - projection
  - simulation
slug: week12
dropCap: no
displayInMenu: no
displayInList: yes
resources:
- name: featuredImage
  src: "vikings_at_broncos.jpg"
  params:
    description: "Vikings at Broncos!"
params:
  week: 12
---

*Last Update: Pos SNF*

<!--more-->

## Game Center

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
# put rnotbook in the same workdir
knitr::opts_knit$set(root.dir = normalizePath(rprojroot::find_rstudio_root_file())) 
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r gameCenterChart, fig.height=4, fig.width=8}
library(tidyverse)
library(glue)

sim <- readRDS("./data/simulations_history.rds") %>% 
  filter(week==params$week) %>%
  filter(timestamp==max(timestamp, na.rm=T)) %>%
  unnest(home.points, away.points, .sep = ".")
  

lastUpdate <- unique(sim$timestamp) 
lastPrefix <- unique(sim$prefix)

sim %>% 
  select(week, timestamp, prefix, 
         contains("logoUrl"),
         contains("name"),
         contains("record"),
         contains("win.prob"),
         contains("pts"),
         contains("Median"),
         contains("minutesRemaining")) %>% 
  mutate( game.id = glue("({away.minutesRemaining} min) {away.name} @ {home.name} ({home.minutesRemaining} min)") ) %>%
  ggplot(aes(x=0)) +
  geom_col(aes(y=home.points.Median), fill="lightgray", width = .7) +
  geom_col(aes(y=home.pts), fill="darkred", width = .5) +
  geom_col(aes(y=-away.points.Median), fill="lightgray", width = .7) +
  geom_col(aes(y=-away.pts), fill="darkblue", width = .5) +
  geom_text(aes(y=home.points.Median, label=round(home.points.Median,2)), size=4,
            hjust = "left", vjust="middle", color="black", nudge_y = 2, nudge_x = .05) +
  geom_text(aes(y=home.pts, label=round(home.pts,2)), size=4,
            hjust = "right", vjust="middle", color="white", nudge_y = -2, nudge_x = .05) +
  geom_text(aes(y=-away.points.Median, label=round(away.points.Median,2)), size=4,
            hjust = "right", vjust="middle", color="black", nudge_y = -2, nudge_x = .05) +
  geom_text(aes(y=-away.pts, label=round(away.pts,2)), size=4,
            hjust = "left", vjust="middle", color="white", nudge_y = 2, nudge_x = .05) +
  coord_flip() +
  facet_wrap(~game.id, ncol = 1) +
  labs(x="", title=glue("Last Update: {lastUpdate} - {lastPrefix}"),
       subtitle = "") +
  xlim(-.5,.5) +
  ylim(-1.1*max(sim$away.points.Median), 1.1*max(sim$home.points.Median)) +
  theme_void() +
  theme( strip.text = element_text(size=12, face = "bold"), 
         plot.margin = unit(c(15,15,15,15),"pt"),
         plot.title = element_text(hjust = .5, size=10),
         plot.subtitle = element_text(hjust = .5))

```


## Projections

* [Individual Players Projections](/reports/ffa_players_projection_week12.html)

## Simulations

* [Pos SNF](/reports/dudes_simulation_week12_posSNF_v4.html)
* [Pre SNF](/reports/dudes_simulation_week12_preSNF_v4.html)
* [Pos TNF](/reports/dudes_simulation_week12_posTNF_v4.html)
* [Pos Waivers](/reports/dudes_simulation_week12_posWaiver_v4.html)
* [Pre Waivers](/reports/dudes_simulation_week12_preWaiver_v4.html)


## Twittersphere

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Look at this amazing <a href="https://twitter.com/hashtag/NFL?src=hash&amp;ref_src=twsrc%5Etfw">#NFL</a> <a href="https://twitter.com/hashtag/NFL100?src=hash&amp;ref_src=twsrc%5Etfw">#NFL100</a> highlight: INTERCEPTION nubmer 4 seals win for Chiefs <a href="https://twitter.com/hashtag/KCvsLAC?src=hash&amp;ref_src=twsrc%5Etfw">#KCvsLAC</a><br><br>Find out more at <a href="https://t.co/ansiKbxdlh">https://t.co/ansiKbxdlh</a> <a href="https://twitter.com/hashtag/NFL?src=hash&amp;ref_src=twsrc%5Etfw">#NFL</a> <a href="https://twitter.com/hashtag/NFL100?src=hash&amp;ref_src=twsrc%5Etfw">#NFL100</a> <a href="https://twitter.com/hashtag/NFLHighlights?src=hash&amp;ref_src=twsrc%5Etfw">#NFLHighlights</a> <a href="https://twitter.com/hashtag/SportsTalkLine?src=hash&amp;ref_src=twsrc%5Etfw">#SportsTalkLine</a> <a href="https://t.co/qET0E9BmAK">pic.twitter.com/qET0E9BmAK</a></p>&mdash; Pro Football Talk Line (@ProFootballTL) <a href="https://twitter.com/ProFootballTL/status/1196834484534042625?ref_src=twsrc%5Etfw">November 19, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


## New Age Analytics

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">ESPN&#39;s QBR through week 11 <a href="https://t.co/AsjYCD7gDa">https://t.co/AsjYCD7gDa</a> <a href="https://t.co/rQyfFVonGs">pic.twitter.com/rQyfFVonGs</a></p>&mdash; new-age analytical (@benbbaldwin) <a href="https://twitter.com/benbbaldwin/status/1196804955153346567?ref_src=twsrc%5Etfw">November 19, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Quarterback predictive composite DAKOTA index ratings through week 11 <a href="https://t.co/pxkq6kx0Aq">pic.twitter.com/pxkq6kx0Aq</a></p>&mdash; new-age analytical (@benbbaldwin) <a href="https://twitter.com/benbbaldwin/status/1196804261025333248?ref_src=twsrc%5Etfw">November 19, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

<blockquote class="twitter-tweet"><p lang="en" dir="ltr">Week 11 NFL Tiers.<br><br>--The Ravens are very, very good<br>--The Cowboys and Vikings are underrated but probably not going to get a playoff bye so likely doomed in the playoffs <a href="https://t.co/U8qq7rHjOc">pic.twitter.com/U8qq7rHjOc</a></p>&mdash; new-age analytical (@benbbaldwin) <a href="https://twitter.com/benbbaldwin/status/1196800790670782464?ref_src=twsrc%5Etfw">November 19, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
